Exploration of clustering results

### 2024-08-09 analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

- SCTransform (default parameters)
- RunPCA (default) 
- RunUMAP (dims = 1:50) 
- FindNeighbors (dims = 1:50) 
- FindClusters (default)

@@

# add metadata from SingleCellExperiment to Seurat
srat@misc <- metadata(sce)

>>>>

- `SCTransform` (default parameters)
- `RunPCA` (default) 
- `RunUMAP` (dims = 1:50) 
- `FindNeighbors` (dims = 1:50) 
- `FindClusters` (default)

@@

# add metadata from SingleCellExperiment to Seurat
srat@misc <- metadata(sce)
rm(sce)
